Hydra battles in Coq

### 2020-09-01 latex/hydras.tex
minor corrections

\begin{tabular}{|c|c|c|c|l|}
\hline
Name & Ascii&Math& Description& Page \\\hline
omega & \texttt{omega} & $\omega$ &   the first infinite ordinal   & \pageref{sect:notation-omega},\dots\\
phi0     & \texttt{phi0 alpha} & $\varphi_0(\alpha),\; \omega^\alpha$&exponential of base $\omega$ & \pageref{sect:notation-phi0}\\

>>>>

\begin{tabular}{|c|c|c|c|l|}
\hline
Name & Ascii&Math& Description& Page \\\hline
F & \texttt{F $n$} & $n$ & The $n$-th finite ordinal &  
\pageref{sect:notation-F}, \pageref{sect:notation-F_sch}\\ 
omega & \texttt{omega} & $\omega$ &   the first infinite ordinal   & \pageref{sect:notation-omega},\dots\\
phi0     & \texttt{phi0 alpha} & $\varphi_0(\alpha),\; \omega^\alpha$&exponential of base $\omega$ & \pageref{sect:notation-phi0}\\
